A Deterministic and Terminating Semantics for the Synchronous Programming Language~\CEU

### 2018-02-18 06-appendix.tex
Adiciona dois teoremas sobre determinismo ao apêndice
Determinismo de n aplicações de \out e \nst

@@

>>>>

\begin{theorem}\label{thm.det-out-pop-n}
  If~$\delta\out[n]\delta_1$ and~$\delta\out[n]\delta_2$
  then~$\delta_1=\delta_2$.
\end{theorem}
\begin{proof}
  By induction on~$n$.
  %%
  The theorem is trivially true for~$n=0$ and follows directly from
  Lemma~\ref{lem.det-out} for~$n=1$.  (Note that, for~$n>1$, the theorem is
  vacuously true for~$\outpush$ transitions.  By the format of
  rules~\R{push} and~\R{pop}, transitions~$\outpush$ cannot be applied more
  than once in a row and cannot occur after a~$\outpop$ transition.)

  Suppose
  \[
    \delta\out[1]\delta_1'\out[n-1]\delta_1
    \quad\text{and}\quad
    \delta\out[1]\delta_2'\out[n-1]\delta_2,
  \]
  for some~$n>1$ and~$\delta_1'$, $\delta_2'\in\Delta$.
  %%
  By Lemma~\ref{lem.det-out}, $\delta_1'=\delta_2'$.  By induction
  hypothesis, $\delta_1=\delta_2$.\qedhere
\end{proof}

@@

\begin{theorem}\label{thm.det-nst-n}
  If~$\delta\nst[n]\delta_1$ and~$\delta\nst[n]\delta_2$
  then~$\delta_1=\delta_2$.
\end{theorem}
\begin{proof}
  Similar to the proof of Theorem~\ref{thm.det-out-pop-n}.
\end{proof}
